Preliminary Survey on Statistics and Software

### 2019-09-06 content/assignment/00-preliminary-survey.Rmd
Fixed icons for survey answer key

- [<i class="fas fa-file-pdf"></i> `Download as PDF`](/homeworks/00-preliminary-survey.pdf)

>>>>

- [<i class="fas fa-file-pdf"></i> `Download as PDF`](/homeworks/00-preliminary-survey.pdf)
- [<i class="fas fa-external-link-square-alt"></i> `Answer Key`](/homeworks/00-preliminary-survey-answers-pdf.pdf)
- [<i class="fas fa-file-pdf"></i> `Answer Key`](/homeworks/00-preliminary-survey-answers.html)
